The demographic costs of sexually antagonistic selection in partially selfing populations

### 2022-01-05 doc/ResponseLetter-R1.tex

\begin{quote}
	{\itshape Thank you for the very encouraging assessment.}
\end{quote}

\noindent I have one main comment:

\noindent-- Discussion: Conclusions are drawn before limitations of the model are mentioned. However, it seems to me that it would be very important to discuss the effect of those limitations on the results themselves and therefore discuss the generality of the results. For instance, what is the potential effect of female dominance in the marriage function on the results and in particular on conclusion of lines 477-480.

\begin{quote}
	{\itshape While we feel that there is strong precedence for discussing the key results of a study before diving into the various caveats for with the analysis, your point is well taken that we need to more clearly acknowledge these limitations in the methods and direct readers to where these limitations are discussed. In our Methods section, we are now careful to point readers to the various Appendixes, Supplements, and places in the Discussion where these limitations are dealt with (e.g., see {\bf L.94--98, 103--109, 128--134, 183--186, 187--189, 196--197, 207--212, 274--275}), and we have added more explicit discussion of several of our key assumptions in the discussion ({\bf e.g., L.519--581}). We discuss both the causes and potential effects of incorporating male-limitation of reproductive success on {\bf L.550--561}}.
\end{quote}

### 2022-01-05 doc/SA-Hermaphrodites-wDemography-R1.tex
Minor typos response letter, second sentence intro
Yay :)

%To persist in the long term, a population must be able to adapt to its environment. Yet, the process of adaptation can be impeded by a variety of genetic and environmental factors, such as deleterious mutations \citep{Haldane1937}, \textcolor{blue}{rapid, unpredictable, or extreme changes} in environmental conditions \citep{Maynard-Smith1976, LandeShannon1996, OrrUnckless2008,Lyberger-etal-2021}, maladaptive gene-flow \citep{KirkpatrickBarton1997, BolnickNosil2007}, and genetic constraints \citep{ConnallonHall2018, MatthewsConnallon2019}. Genetic constraints on adaptation can arise as a consequence of conflicting selection and gene-flow between different classes of individuals, or more generally, when \textcolor{blue}{different fitness components are negatively correlated} \citep{CharlesworthHughes2000, ConnallonHall2018}. 
\textcolor{blue}{A population's ability to adapt to its environment and persist in the long term depends upon the genetic variation that it carries \citep{Fisher1930, Lewontin1975}. Yet, populations are heterogenous collections of individuals existing in a complex world where adaptation can be impeded by conflicting selection and gene-flow between different classes of individuals, or more generally, when different fitness components are negatively correlated \citep{Prout2000, CharlesworthHughes2000, ConnallonHall2018}.}

>>>>

%To persist in the long term, a population must be able to adapt to its environment. Yet, the process of adaptation can be impeded by a variety of genetic and environmental factors, such as deleterious mutations \citep{Haldane1937}, \textcolor{blue}{rapid, unpredictable, or extreme changes} in environmental conditions \citep{Maynard-Smith1976, LandeShannon1996, OrrUnckless2008,Lyberger-etal-2021}, maladaptive gene-flow \citep{KirkpatrickBarton1997, BolnickNosil2007}, and genetic constraints \citep{ConnallonHall2018, MatthewsConnallon2019}. Genetic constraints on adaptation can arise as a consequence of conflicting selection and gene-flow between different classes of individuals, or more generally, when \textcolor{blue}{different fitness components are negatively correlated} \citep{CharlesworthHughes2000, ConnallonHall2018}. 
\textcolor{blue}{A population's ability to adapt to its environment and persist in the long term depends upon the genetic variation that it carries \citep{Fisher1930, Lewontin1975}. Yet, populations are heterogenous collections of individuals existing in a complex world where adaptation can be impeded by conflicting selection and gene-flow between different classes of individuals \citep{Prout2000, CharlesworthHughes2000, ConnallonHall2018}.}
